gij bent 2

### 2024-12-09 paper/paper.qmd
Fix posthoc table

format_posthoc_table <- function(df) {
  df <- df$contrasts %>% tidy()
  df$term <- NULL
  df$df <- NULL
  df$null <- NULL
  df$null.value <- NULL
  df$contrast <- gsub("[()]", "", df$contrast)
  df$contrast <- gsub("-", "↔", df$contrast)

@@

```{r #fig-gender-violin}
#| fig-cap: A violin plot describing the individual variation coefficients for men and women. A wider figure means more data for that y value.
coefficients %>%
  ggplot(aes(x = gender, y = coefficient, fill = gender)) +
  geom_violin() +
  geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
```

@@

```{r #fig-region-violin}
#| fig-cap: A violin plot describing the individual variation coefficients by region. A wider figure means more data for that y value.
coefficients %>%
  ggplot(aes(x = dialect, y = coefficient, fill = dialect)) +
  geom_violin() +
  geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
```

@@

```{r #tbl-linear-predictors}
#| tbl-cap: "Results of the linear regression analysis. * indicates statistical significance"
fit <- lm(coefficient ~ gender + dialect + influence, data=coefficients %>% no_unknown_gender())
fit %>% format_table()
```

@@

posthoc %>% format_posthoc_table()
```

>>>>

format_posthoc_table <- function(df) {
  df <- df$contrasts %>% tidy()
  df$term <- NULL
  df$df <- NULL
  df$null <- NULL
  df$null.value <- NULL
  df$contrast <- gsub("[()]", "", df$contrast)
  df$contrast <- gsub(" - ", " ↔ ", df$contrast)

@@

```{r #fig-gender-violin}
#| fig-cap: A violin plot describing the individual variation coefficients for men and women. A wider figure means more data for that y value.
coefficients$gender_friendly <- gsub("(_is_gender_)", "", coefficients$gender)
coefficients$gender_friendly <- factor(coefficients$gender_friendly, levels=c("male", "female"))

coefficients %>%
  ggplot(aes(x = gender_friendly, y = coefficient, fill = gender_friendly)) +
  geom_violin() +
  xlab("gender") +
  guides(fill=guide_legend(title="gender")) +
  geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
```

@@

```{r #fig-region-violin}
#| fig-cap: A violin plot describing the individual variation coefficients by region. A wider figure means more data for that y value.
coefficients$dialect_friendly <- gsub("(_is_dialect_)", "", coefficients$dialect)
#coefficients$gender_friendly <- factor(coefficients$gender_friendly, levels=c("male", "female"))

coefficients %>%
  ggplot(aes(x = dialect_friendly, y = coefficient, fill = dialect_friendly)) +
  geom_violin() +
  xlab("dialect area") +
  guides(fill=guide_legend(title="dialect area")) +
  geom_hline(yintercept=0, color="black", linewidth=1, linetype="dotdash")
```

@@

```{r #tbl-linear-predictors}
#| tbl-cap: "Results of the linear regression analysis. * indicates statistical significance"
fit <- lm(coefficient ~ gender + dialect + influence, data=coefficients %>% no_unknown_gender())
coefficients_lm_df <- fit %>% format_table()

coefficients_lm_df$term <- gsub("(gender_)", "", coefficients_lm_df$term)
coefficients_lm_df$term <- gsub("(_is_dialect_)", "", coefficients_lm_df$term)

coefficients_lm_df
```

@@

posthoc_df <- posthoc %>% format_posthoc_table()
posthoc_df$contrast <- gsub("(_is_dialect_)", "", posthoc_df$contrast)

posthoc_df
```
